20220426_main_plot_t_test

### 2022-04-27 exploratory/20220426_main_plot_t_test.Rmd
fine-tuned the t-test output table, close #5

# effect size
casual_d <- 
  casual_long %>% 
  nest_by(homosexual_dlikelihood_dstandard) %>% 
  mutate(
    inpool.d = cohens_d(inpool ~ gender, data = data) %>% pull(Cohens_d),
    outpool.d = cohens_d(outpool ~ gender, data = data) %>% pull(Cohens_d),
    exp_all.d = cohens_d(exp_all ~ gender, data = data) %>% pull(Cohens_d),
    exp_ip.d = cohens_d(exp_ip ~ gender, data = data) %>% pull(Cohens_d),
    partner_all.d = cohens_d(partner_all ~ gender, data = data) %>% pull(Cohens_d),
    partner_ip.d = cohens_d(partner_ip ~ gender, data = data) %>% pull(Cohens_d)
    )

# combine the descriptives, test results, and effect size
full_join(casual_des, casual_t_test, casual_d, by = "homosexual_dlikelihood_dstandard") %>% 
  kable()
```

>>>>

# effect size
casual_d <- 
  casual_long %>% 
  nest_by(homosexual_dlikelihood_dstandard) %>% 
  mutate(
    inpool.d = cohens_d(inpool ~ gender, data = data) %>% pull(Cohens_d),
    outpool.d = cohens_d(outpool ~ gender, data = data) %>% pull(Cohens_d),
    exp_all.d = cohens_d(exp_all ~ gender, data = data) %>% pull(Cohens_d),
    exp_ip.d = cohens_d(exp_ip ~ gender, data = data) %>% pull(Cohens_d),
    partner_all.d = cohens_d(partner_all ~ gender, data = data) %>% pull(Cohens_d),
    partner_ip.d = cohens_d(partner_ip ~ gender, data = data) %>% pull(Cohens_d)
    ) %>% 
  select(-data)

# combine the descriptives, test results, and effect size
full_join(casual_des, casual_t_test, by = "homosexual_dlikelihood_dstandard") %>% 
  full_join(., casual_d, by = "homosexual_dlikelihood_dstandard") %>% 
  kable()
```
